Paper

### 2018-02-05 Paper.Rmd
...

globalnHGDCN.plot = cn.mtn.plot(subset(globalCNdf, seg.type != 'arms' & Pathology %in% c('LGD','HGD','IMC')), labeller(Status=dys.status, chr=label_value)) + labs(title='LGD/HGD/IMC Only')

@@

globalCN.plot + theme(legend.position = 'none')

globalnHGDCN.plot + theme(legend.position = 'none')

globalBECN.plot + theme(legend.position = 'none')

@@

# m = melt(insilico.rocs, measure.vars = 'auc')
# ggplot(m, aes(variable,value)) + ylim(0,1) +
#   geom_boxplot(fill='mintcream', color='grey55') + geom_jitter(width=0.2, color='darkblue', size=1.5, show.legend = F) + 
#   geom_text(data=subset(m, value %in% range(value)), aes(label=round(value,2)), vjust=0.02, hjust=0.2) +
#   plot.theme + labs(x='',y='AUC',title='AUC', subtitle='20 insilico 20:69 splits')

@@

```{r prediction_cutoff, echo=F, message=F, warning=F, fig.height=7, fig.width=7}
preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
roc$model = 'CN Model'

multi.roc.plot(list(roc), colors=brewer.pal(3,'Greys')[3]) + labs(title='Discovery cohort ROC')

insilico.rocs = rbind(insilico.rocs, c(pROC::ci.auc(roc), pROC::coords(roc, 'best')))

insilico.rocs[1:20,'split'] = paste('in-silico', 1:20)
insilico.rocs[21,'split'] = 'discovery'

ggplot(insilico.rocs, aes(split, auc)) + geom_point() + ylim(0,1) +
  geom_errorbar(aes(ymin=auc.ci.min, ymax=auc.ci.max), width=0.2) + 
  coord_flip() + plot.theme + labs(y='AUC', x='', title='AUC per split', subtitle='20 insilico 20:69 splits')

@@

pathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('LGD','HGD','IMC'), 1, 0) )
pathroc$model = 'Dysplasia (HGD & LGD)'

@@

### Per Endoscopy ROCs
```{r, echo=F, warning=F, message=F,fig.height=4, fig.width=4}

pendo = do.call(rbind, pg.samp) %>% group_by(Patient, Status, Hospital.Research.ID, PID ) %>% summarise(
  'max'=max(Prediction), 'avg'=mean(Prediction), 'n'=length(PID)
)

@@

get.auc.at<-function(roc, foc='spec', p=c(1,0.99)) {
# To find the auc at a given spec or sens
  pROC::auc(roc, partial.auc=p, partial.auc.focus=foc, partial.auc.correct=T)

}

@@

m = rbind.data.frame(
      get.roc.stat(p53roc),
      get.roc.stat(hgdpathroc),
      get.roc.stat(pathroc),
      get.roc.stat(roc, 0.6))
m$model = factor(m$model, levels=c('p53 IHC','HGD Only','Dysplasia (HGD & LGD)','CN Model'), ordered = T)

@@

cols = brewer.pal(11, "PRGn")
dodge = position_dodge(width=0.9)
ggplot(melt(subset(m, Measure == 'AUC'), measure.vars='value'), aes(x=model, y=value*100, ymin=CI.min*100, ymax=CI.max*100, group=Measure, fill=Measure)) + 
  geom_bar(stat='identity',position=dodge) + geom_errorbar(position=dodge, width=0.3, color='black' ) + 
  geom_text(aes(label=paste(round(value,2)*100,'%',sep=''), y=1, vjust=-1 ), position=dodge, color='white')  +
  scale_fill_manual(values=cols, name='') + plot.theme + 
  theme(legend.position = 'none', axis.text.x = element_text(angle=45, hjust=1)) + labs(x='', y='AUC', title='ROC Comparison')

@@

```{r pcalib, echo=F, warning=F, message=F, fig.width=8, fig.height=6}
ggplot(pred.confidence, aes(mn, perc)) + 
  geom_rect(aes(xmin=r1, xmax=r2, ymin=0,ymax=1, fill=Risk), alpha=0.6) + scale_fill_manual(values=riskCols) +
  geom_point() + geom_text(aes(label=paste(r1,r2,sep='-')), nudge_x=0.05) +
  geom_errorbar(aes(ymin=ci.low, ymax=ci.high), width=0.01) + labs(x='Mean prediction', y='Ratio of `P` patients', title='Prediction calibration') +
  scale_color_manual(values=riskCols) + plot.theme + theme(legend.position = 'none')
```

@@

ggplot(back, aes(OR)) + geom_histogram(aes(fill=..x..), bins=10, show.legend = F) +
  #scale_fill_distiller(palette = 'RdYlBu', type='div',name='P(P)') +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(y='n Samples', x='Relative Risk', title='Unadjusted relative risk') + plot.theme

ggplot(back, aes(Prediction)) + geom_histogram(aes(fill=..x..), breaks=cuts, show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
  #scale_fill_distiller(palette = 'RdYlBu', type='div',name='P(P)') +
    plot.theme + labs(title='Predictions, all samples model', y='n Samples', x='Probability')

@@

min.theme = theme(text=element_text(size=10), panel.background=element_blank(), strip.background=element_rect(fill="grey97"), 
                   strip.text = element_text(size=10), axis.text = element_blank(),
                   axis.line=element_line(color='black'), panel.grid.major.y =element_line(color='grey95'), panel.grid.major.x = element_blank(),
                   panel.border = element_rect(color="grey", fill=NA, size=0.5), panel.spacing.x = unit(0, 'lines'), panel.spacing.y = unit(0.1, 'lines')   )

@@

  p = ggplot(df, aes(x=chr.length)) + facet_grid(Endoscopy.Year+ogj~chr, scales='free', space='free_x', labeller = labeller(.multi_line=F)) +
      geom_rect(aes(xmin=start, xmax=end, ymin=0, ymax=mean.value, fill=ogj), show.legend=T) + 
      scale_fill_manual(values=pal, limits=limits,  name='OGJ Dist.') +
      labs(title=title, x='') + min.theme

@@

p1 = mtn.spatial(subset(globalCNdf, Patient == 48 & seg.type != 'arms'), back, ogjLimits, 'Patient 48 (P)')
p2 = mtn.spatial(subset(globalCNdf, Patient == 20 & seg.type != 'arms'), back, ogjLimits,'Patient 20 (P)' )
p3 = mtn.spatial(subset(globalCNdf, Patient == 60 & seg.type != 'arms'), back, ogjLimits,'Patient 60 (P)' )

p4 = mtn.spatial(subset(globalCNdf, Patient == 3 & seg.type != 'arms'), back,ogjLimits,'Patient 3 (NP)' )
p5 = mtn.spatial(subset(globalCNdf, Patient == 15 & seg.type != 'arms'), back,ogjLimits,'Patient 15 (NP)' )
p6 = mtn.spatial(subset(globalCNdf, Patient == 51 & seg.type != 'arms'), back,ogjLimits,'Patient 51 (NP)' )

@@

grid.arrange(p1$legend)

@@

ggplot(riskPath, aes(Pathology, ratio*100)) + geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) + 
  scale_fill_manual(values=riskCols) + scale_color_manual(values=c('white','black','white')) +
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101), position=position_stack(), size=4) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), size=5, show.legend = F) +
  facet_grid(~Status) + plot.theme + labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')

@@

p53Path$p53.Status = factor(p53Path$p53.Status, ordered = T)
p53Path = arrange(p53Path, Pathology, p53.Status)
col = brewer.pal(11, "PRGn")[c(9,3)]
ggplot(p53Path, aes(Pathology, ratio*100, group=Pathology, fill=p53.Status)) + geom_bar(stat='identity', position = position_stack()) +
  scale_fill_manual(values=col, name='p53 IHC', labels=c('Normal','Aberrant')) + 
  geom_text(aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101)) +
  geom_text(aes(label=paste(ratio*100,'%',sep='')), position=position_stack(vjust = 0.5), size=5) +
  plot.theme + labs(title='Samples predicted by aberrant p53 IHC', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')

@@

ggplot(endos.m, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,105) +
  geom_bar(stat='identity', fill='darkred', alpha=0.8, show.legend = F) + 
  geom_errorbar(color='grey21', width=0.2) +
  geom_text(aes(y=3, label=paste(round(pred.r*100), '%', sep='')), color='white') +
  geom_text(aes(y=pred.r*100-5, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='Predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  plot.theme + theme( axis.text.x=element_text(angle=45,hjust=1))

@@

pred.tiles(subset(back, Patient %in% c(6)), ncol=1, cols=myPal, probs=T, OR=F) + labs(title='') + theme(legend.position = 'none')
pred.tiles(subset(back, Patient %in% c(48)), ncol=1, cols=myPal, probs=T) + labs(title='') + theme(legend.position = 'none')
pred.tiles(subset(back, Patient %in% c(33)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
pred.tiles(subset(back, Patient %in% c(89)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
```

@@

p = pred.tiles(transform(subset(back, Status == 'NP'), Patient=reorder(Patient, pred.ratio)), cols=myPal, probs=T, nrow=2) + labs(title='Non-Progressors') 
riskLegend = get.legend(p)
p = p + theme(legend.position = 'none')
ggsave('npg_heatmap.png', plot = p, scale = 1, width = 52, height = 8, units = "in", limitsize = F, dpi = 300)

p = pred.tiles(transform(subset(back, Status == 'P'), Patient=reorder(Patient, -pred.ratio)), probs=T, cols=myPal,nrow=2) + labs(title='Progressors') + theme(legend.position = 'none')
ggsave('pg_heatmap.png', plot = p, scale = 1, width = 52, height = 8, units = "in", limitsize = F, dpi = 300)

ggsave('risk_legend.png', plot=grid.arrange(riskLegend), scale=1, dpi=300)

@@

ov = findOverlaps(chGR, genesGR)
genes = as.data.frame(genesGR[unique(subjectHits(ov))])
colnames(genes)[1] = c('chr')

plot.cn.chr(globalCNdf, chrom='17', chr.lengths, genes=genes, haz=chh) + labs(
title="Segment Values Samples", subtitle=paste('NonP:Prog - ', paste(table(patient.info$Status), collapse=':'))) + theme(legend.position = 'none')
```

@@

length(which(round((subset(distanceTSG, distanceToTSG > 0)$distanceToTSG/5e6)-0.5) == round((avgTSGdist/5e6)-0.5)))

@@

cn.mtn.plot(subset(valCNdf, seg.type != 'arms'), labeller(Status=n.status, chr=label_value))

@@

```{r echo=F, warning=F, message=F, fig.height=5,fig.width=25}
pred.tiles(subset(back.v, Status == 'P'), cols=myPal, probs=T, nrow=1) + labs(title='Validation Progressors') + theme(legend.position = 'none')
pred.tiles(subset(back.v, Status == 'NP'), cols=myPal, probs=T, nrow=1) + labs(title='Validation Non-Progressors') + theme(legend.position = 'none')
```

@@

ggplot(riskPath, aes(Pathology, ratio*100)) + geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) +   scale_fill_manual(values=riskCols) + scale_color_manual(values=c('white','black','white')) + 
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101), position=position_stack(), size=4, show.legend = F) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), size=5, show.legend = F) +
  facet_grid(~Status) + plot.theme + labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')

@@

```{r, echo=F, warning=F, message=F, fig.width=8, fig.height=5}
vign.pts = as_tibble(subset(sum.patient.data, Patient %in% c(3, 33, 34, 49, 56, 20), select=c('Status','Patient','age.diagnosis', 'smoking', 'C','M', 'initial.endo','final.endo', 'total.endos','total.samples')))
colnames(vign.pts) = c('Status','Patient','Age at Diagnosis','Smoker','Circumference', 'Maximal length', 'Intial Endoscopy','Final Endoscopy', 'Total Endoscopies','Total Samples')

## P
p = vig.plot(df=subset(back, Patient == 34),info= subset(patient.info, Patient == 34),cols=riskCols) + theme(legend.position = 'bottom')
vigLeg = get.legend(p)
p + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 56), subset(patient.info, Patient == 56),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 20), subset(patient.info, Patient == 20),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 86), subset(patient.info, Patient == 86),cols=riskCols) + theme(legend.position = 'none')

## NP
vig.plot(subset(back, Patient == 3), subset(patient.info, Patient == 3),cols=riskCols) + theme(legend.position = 'none')
vig.plot(df=subset(back, Patient == 23),info= subset(patient.info, Patient == 23),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 33), subset(patient.info, Patient == 33),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 49), subset(patient.info, Patient == 49),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 51), subset(patient.info, Patient == 51),cols=riskCols) + theme(legend.position = 'none')

vig.plot(subset(back, Patient == 6), subset(patient.info, Patient == 6),cols=riskCols) + theme(legend.position = 'none')
vig.plot(subset(back, Patient == 54), subset(patient.info, Patient == 54),cols=riskCols) + theme(legend.position = 'none')
```

```{r, echo=F, warning=F, message=F, fig.width=4, fig.height=1}
grid.arrange(vigLeg)
```

>>>>

#globalnHGDCN.plot = cn.mtn.plot(subset(globalCNdf, seg.type != 'arms' & Pathology %in% c('LGD','HGD','IMC')), labeller(Status=dys.status, chr=label_value)) + labs(title='LGD/HGD/IMC Only')

@@

gp = globalCN.plot + theme(legend.position = 'none') + labs(y='mean adj. seg.', title='All samples') + theme(text=element_text(size=12))
ggsave(filename='plots/globalCN.png', plot=gp, width=16, height=4.6, units='in', dpi=300)

#globalnHGDCN.plot + theme(legend.position = 'none')

gbe = globalBECN.plot + theme(legend.position = 'none') + labs(y='mean adj.seg.', title="Non-Dysplastic Barrett's Samples") + theme(text=element_text(size=12))
ggsave(filename='plots/globalBECN.png', plot=gbe, width=16, height=4.6, units='in', dpi=300)

@@

@@

```{r prediction_cutoff, echo=F, message=F, warning=F, fig.height=7, fig.width=7}
preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
roc$model = 'discovery'
roc$is = 'discovery'

droc = multi.roc.plot(list(roc), colors=brewer.pal(3,'Greys')[3]) + labs(title='Discovery cohort ROC')
ggsave(filename='plots/discovery_roc.png', plot=droc, width=6, height=4, units='in', dpi=300)

insilico.rocs[['discovery']] = roc

df = do.call(rbind, lapply(insilico.rocs, function(r) 
    cbind.data.frame('Specificity'=rev(r$specificities), 'Sensitivity'=rev(r$sensitivities),'model'=r$model, 'is'=r$is) 
))

p = ggplot(df, aes(Specificity, Sensitivity,color=is)) + geom_line(size=1) + 
    geom_line(data=subset(df, model == 'discovery'), color='red', size=1) +
    scale_x_reverse() +
    scale_color_brewer(palette='Blues') +
    labs(title='ROC, all splits', x='Specificity (FPR)', y='Sensitivity (TPR)')  + plot.theme +
    theme(legend.position = 'none')
p

ggsave(filename='plots/splits_roc.png', plot=p, width=6, height=6, units='in', dpi=300)

ir = ggplot(insilico.rocs, aes(is, auc, color=split)) + ylim(0,1) +
  geom_hline(data=m, aes(yintercept=auc, linetype=line), color='grey32', show.legend=F) + 
  geom_point(size=2) + geom_errorbar(aes(ymin=auc.ci.min, ymax=auc.ci.max), width=0.3) + 
  geom_text(data=m, aes(label=paste(variable, round(auc, 2), sep='\n')), color='grey32', nudge_y=0, show.legend=F) + 
  scale_linetype_manual(values=c('dotdash','longdash')) +
  plot.theme + scale_color_brewer(palette='Set1', name='Type') +
  theme(axis.text.x=element_blank(), legend.position = 'bottom') +
  labs(y='AUC', x='Data splits', title='AUC per split', subtitle='20 insilico 20:69 splits')
ir
ggsave(filename='plots/auc_splits.png', plot=ir, width=7, height=8, units='in', dpi=300)

@@

pathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('LGD','HGD','IMC'), 1, 0) )
pathroc$model = 'HGD & LGD'

@@

### Per Endoscopy ROCs
```{r, echo=F, warning=F, message=F,fig.height=4, fig.width=4}
pendo = do.call(rbind, pg.samp) %>% group_by(Patient, Status, Hospital.Research.ID, PID ) %>% summarise(
  'max'=max(Prediction), 'avg'=mean(Prediction), 'n'=length(PID)
)

@@

get.auc.at<-function(roc, foc='spec', p=c(1,0.99)) {
# To find the auc at a given spec or sens
  pROC::auc(roc, partial.auc=p, partial.auc.focus=foc, partial.auc.correct=T)
}

@@

m = rbind.data.frame(
      get.roc.stat(p53roc),
      get.roc.stat(hgdpathroc),
      get.roc.stat(pathroc),
      get.roc.stat(roc))
m$model = factor(m$model, levels=c('p53 IHC','HGD Only','HGD & LGD','CN Model'), ordered = T)

@@

cols = brewer.pal(4, "PRGn")
dodge = position_dodge(width=0.9)

comp = ggplot(melt(subset(m, Measure == 'AUC'), measure.vars='value'), aes(x=model, y=value*100, ymin=CI.min*100, ymax=CI.max*100, group=Measure, fill=Measure)) + 
  geom_bar(stat='identity',position=dodge) + geom_errorbar(position=dodge, width=0.3, color='black' ) + 
  geom_text(aes(y=(value*100)-4, label=paste(round(value,2)*100,'%',sep='')), position=dodge, color='white')  +
  scale_fill_manual(values=cols, name='') + plot.theme + 
  theme(legend.position = 'none', axis.text.x = element_text(angle=45, hjust=1)) + labs(x='', y='AUC', title='ROC Comparison') 
comp

ggsave('plots/compare_auc.png', plot=comp, width=6, height=8, units="in", limitsize=F, dpi = 300)

@@

```{r pcalib, echo=F, warning=F, message=F, fig.width=8, fig.height=6}
pcal = ggplot(pred.confidence, aes(mn, perc)) + 
  geom_rect(aes(xmin=r1, xmax=r2, ymin=0,ymax=1, fill=Risk), alpha=0.6) + scale_fill_manual(values=riskCols) +
  geom_point() + #geom_text(aes(label=paste(r1,r2,sep='-')), nudge_x=0.05) +
  geom_errorbar(aes(ymin=ci.low, ymax=ci.high), width=0.01) + labs(x='Mean prediction', y='Ratio of `P` patients', title='Prediction calibration') +
  scale_color_manual(values=riskCols) + plot.theme + theme(legend.position = 'none', text=element_text(size=10))
pcal

ggsave(filename='plots/pred_calib.png', plot=pcal, width=6, height=6, units='in', dpi=300)
```

@@

unadjRR = ggplot(back, aes(OR)) + geom_histogram(aes(fill=..x..), bins=10, show.legend = F) +
  #scale_fill_distiller(palette = 'RdYlBu', type='div',name='P(P)') +
  scale_fill_gradientn(colors = myPal,  name='') + 
  labs(y='n Samples', x='Relative Risk', title='Unadjusted relative risk') + plot.theme
unadjRR

ggsave(filename='plots/unadj_relrisk.png', plot=unadjRR, width=6, height=5, units='in', dpi=300)

predhist = ggplot(back, aes(Prediction)) + geom_histogram(aes(fill=..x..), breaks=cuts, show.legend = F) +
    scale_fill_gradientn(colors = myPal,  name='') + 
  #scale_fill_distiller(palette = 'RdYlBu', type='div',name='P(P)') +
    plot.theme + labs(title='Predictions, all samples model', y='n Samples', x='Probability') 
predhist

ggsave(filename='plots/pred_hist.png', plot=predhist, width=5, height=5, units='in', dpi=300)

@@

min.theme = theme(text=element_text(size=8), panel.background=element_blank(), strip.background=element_rect(fill="grey97"), strip.text.y = element_text(size=6),
                   strip.text.x = element_text(size=12), axis.text = element_blank(), axis.ticks = element_blank(),
                   axis.line=element_line(color='black'), panel.grid.major.y =element_line(color='grey95'), panel.grid.major.x = element_blank(),
                   panel.border = element_rect(color="grey", fill=NA, size=0.5), panel.spacing.x = unit(0, 'lines'), panel.spacing.y = unit(0.1, 'lines')   )

@@

  blanklabel <- function(s) {
    return('')
  }

  p = ggplot(df, aes(x=chr.length)) + facet_grid(Endoscopy.Year+ogj~chr, scales='free', space='free_x', labeller = labeller(.multi_line = F)) +
      geom_rect(aes(xmin=start, xmax=end, ymin=0, ymax=mean.value, fill=ogj), show.legend=T) + 
      scale_fill_manual(values=pal, limits=limits,  name='OGJ Dist.') +
      labs(title=title, x='') + min.theme

@@

#p1 = mtn.spatial(subset(globalCNdf, Patient == 48 & seg.type != 'arms'), back, ogjLimits, 'Patient 48 (P)')
p2 = mtn.spatial(subset(globalCNdf, Patient == 20 & seg.type != 'arms'), back, ogjLimits,'Patient 20 (P)' )
#p3 = mtn.spatial(subset(globalCNdf, Patient == 60 & seg.type != 'arms'), back, ogjLimits,'Patient 60 (P)' )

#p4 = mtn.spatial(subset(globalCNdf, Patient == 3 & seg.type != 'arms'), back,ogjLimits,'Patient 3 (NP)' )
#p5 = mtn.spatial(subset(globalCNdf, Patient == 15 & seg.type != 'arms'), back,ogjLimits,'Patient 15 (NP)' )
p6 = mtn.spatial(subset(globalCNdf, Patient == 51 & seg.type != 'arms'), back,ogjLimits,'Patient 51 (NP)' )

@@

grid.arrange(p2$legend)

ggsave(filename='plots/spatial_mtn_pt20.png', plot=grid.arrange(p2$grob), width=14, height=6, units='in', dpi=300)
ggsave(filename='plots/spatial_mtn_pt51.png', plot=grid.arrange(p6$grob), width=14, height=6, units='in', dpi=300)

@@

rp = ggplot(riskPath, aes(Pathology, ratio*100)) + geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) + 
  scale_fill_manual(values=riskCols) + scale_color_manual(values=c('white','black','white')) +
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101), position=position_stack(), size=4) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), size=5, show.legend = F) +
  facet_grid(~Status) + plot.theme + labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom', text=element_text(size=10))
rp

ggsave(filename='plots/pred_by_path.png', plot=rp, width=9, height=7, units='in', dpi=300)

@@

p53Path$p53.Status = factor(p53Path$p53.Status, ordered = T)
p53Path = arrange(p53Path, Pathology, p53.Status)
col = brewer.pal(11, "PRGn")[c(10,2)]
rp = ggplot(p53Path, aes(Pathology, ratio*100, group=Pathology, fill=p53.Status)) + geom_bar(stat='identity', position = position_stack()) +
  scale_fill_manual(values=col, name='p53 IHC', labels=c('Normal','Aberrant')) + 
  geom_text(aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101)) +
  geom_text(aes(label=paste(ratio*100,'%',sep='')), position=position_stack(vjust = 0.5), size=5,color='white') +
  plot.theme + labs(title='Samples predicted by aberrant p53 IHC', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')
rp
ggsave(filename='plots/p53_pred.png', plot=rp, width=7, height=6, units='in', dpi=300)

@@

rp = ggplot(endos.m, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,105) +
  geom_bar(stat='identity', fill='darkred', alpha=0.8, show.legend = F) + 
  geom_errorbar(color='grey21', width=0.2) +
  geom_text(aes(y=3, label=paste(round(pred.r*100), '%', sep='')), color='white') +
  geom_text(aes(y=pred.r*100-5, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='Predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  plot.theme + theme( axis.text.x=element_text(angle=45,hjust=1), text=element_text(size=12))

ggsave(filename='plots/pred_endo.png', plot=rp, width=9, height=7, units='in', dpi=300)

@@

#pred.tiles(subset(back, Patient %in% c(6)), ncol=1, cols=myPal, probs=T, OR=F) + labs(title='') + theme(legend.position = 'none')
#pred.tiles(subset(back, Patient %in% c(48)), ncol=1, cols=myPal, probs=T) + labs(title='') + theme(legend.position = 'none')
#pred.tiles(subset(back, Patient %in% c(33)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
#pred.tiles(subset(back, Patient %in% c(89)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
```

@@

p1 = pred.tiles(subset(back, Status == 'NP'), cols=myPal, probs=T, nrow=2) + labs(title='Non-Progressors') 
riskLegend = get.legend(p1)
p1 = p1 + theme(legend.position = 'bottom')
riskLegendLong = get.legend(p1)

p1 = p1 + theme(legend.position = 'none')

p2 = pred.tiles(subset(back, Status == 'P'), probs=T, cols=myPal,nrow=2) + labs(title='Progressors') + theme(legend.position = 'none')

ggsave('plots/pred_heatmap.png', plot=grid.arrange(p2,p1,nrow=2), width=52, height=16, units="in", limitsize=F, dpi = 300)

ggsave('plots/npg_heatmap.png', plot=p1, width=52, height=8, units="in", limitsize=F, dpi = 300)
ggsave('plots/pg_heatmap.png', plot=p2, width=52, height=8, units="in", limitsize=F, dpi = 300)

ggsave('plots/risk_legend.png', plot=grid.arrange(riskLegend), width=2,height=4, dpi=300)

ggsave('plots/risk_legend_long.png', plot=grid.arrange(riskLegendLong), width=8,height=2, dpi=300)

@@

ov = findOverlaps(chGR, genesGR)
#genes = as.data.frame(genesGR[unique(subjectHits(ov))])
#colnames(genes)[1] = c('chr')

g17 = plot.cn.chr(globalCNdf, chrom='17', chr.lengths, genes=genes, haz=chh, label=labeller(chr=label_both, Status=n.status)) + labs(
title="All Samples") + theme(legend.position = 'none')
g17

g17 = g17 + theme(text=element_text(size=11), strip.text = element_text(size=11))
ggsave(filename='plots/chr17.png', plot=g17, width=10, height=5, units='in', dpi=300)

@@

length(which(round((subset(distanceTSG, distanceToTSG > 0)$distanceToTSG/5e6)-0.5) == round((avgTSGdist/5e6)-0.5)))
```

@@

cn.mtn.plot(subset(valCNdf, seg.type != 'arms'), labeller(Status=n.status, chr=label_value)) + theme(legend.position = 'none')

@@

```{r echo=F, warning=F, message=F, fig.height=10,fig.width=25}
back.v$Patient = factor(as.numeric(back.v$Patient), ordered=T)

p1 = pred.tiles(subset(back.v, Status == 'P'), cols=myPal, probs=T, nrow=1) + labs(title='Validation Progressors', x='') + theme(legend.position = 'bottom') 
valLeg = get.legend(p1)
p1 = p1 + theme(legend.position = 'none')
p2 = pred.tiles(subset(back.v, Status == 'NP'), cols=myPal, probs=T, nrow=1) + labs(title='Validation Non-Progressors') + theme(legend.position = 'none')

grid.arrange(p1, p2, nrow=2)

ggsave(filename='plots/val_heatmap.png', plot=grid.arrange(p1, p2, nrow=2), width=18, height=6, units='in', dpi=300)

ggsave(filename='plots/val_leg.png', plot=valLeg, width=4, height=2, units='in', dpi=300)

@@

pr = ggplot(riskPath, aes(Pathology, ratio*100)) + geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) +   scale_fill_manual(values=riskCols) + scale_color_manual(values=c('white','black','white')) + 
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=101), position=position_stack(), size=4, show.legend = F) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), size=5, show.legend = F) +
  facet_grid(~Status) + plot.theme + labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')
pr

ggsave(filename='plots/val_riskpath.png', plot=pr, width=7, height=7, units='in', dpi=300)

@@

```{r, echo=F, warning=F, message=F, fig.width=5, fig.height=5}
vign.pts = as_tibble(subset(sum.patient.data, Patient %in% c(3, 33, 34, 49, 56, 20), select=c('Status','Patient','age.diagnosis', 'smoking', 'C','M', 'initial.endo','final.endo', 'total.endos','total.samples')))
colnames(vign.pts) = c('Status','Patient','Age at Diagnosis','Smoker','Circumference', 'Maximal length', 'Intial Endoscopy','Final Endoscopy', 'Total Endoscopies','Total Samples')

## P
p = vig.plot(df=subset(back, Patient == 34),info= subset(patient.info, Patient == 34),cols=riskCols) + theme(legend.position = 'bottom')
vigLeg = get.legend(p)
p = p + theme(legend.position = 'none')
ggsave('plots/vig_34.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 56), subset(patient.info, Patient == 56),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_56.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 20), subset(patient.info, Patient == 20),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_20.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 86), subset(patient.info, Patient == 86),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_86.png', plot=p, width=6, height=6,dpi=300)

print(p)

## NP
p = vig.plot(subset(back, Patient == 3), subset(patient.info, Patient == 3),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_3.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(df=subset(back, Patient == 23),info= subset(patient.info, Patient == 23),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_23.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 33), subset(patient.info, Patient == 33),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_33.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 49), subset(patient.info, Patient == 49),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_49.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 51), subset(patient.info, Patient == 51),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_51.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 6), subset(patient.info, Patient == 6),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_6.png', plot=p, width=6, height=6,dpi=300)

p = vig.plot(subset(back, Patient == 54), subset(patient.info, Patient == 54),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vig_54.png', plot=p, width=6, height=6,dpi=300)

print(p)
